% !TEX root = ../dkilleffer-thesis-proposal.tex
%
\chapter{Risks and Alternatives}
\label{sec:risksandalternatives}



%Describe the development environment you require (language, OS, system) and other tools you expect to use.  Also describe any assumptions you have made about what it will take to finish your work.

%Describe the risks you now see as inherent in your work and alternatives you might have to take to ameliorate these risks (e.g., project scope and alternatives for scope reduction)


I will primarily be using Apple MacBook Pro laptops for the development of this project, currently running OS X 10.11.x El Capitan.  With respect to tooling, I will be using WebStorm as my IDE of choice because it offers a rich development environment for JavaScript projects and I am already very familiar with it.  Source code will be kept up to date in a personal GitHub repository so that I can synchronize my work between the two primary laptops I will be using, as well as to keep myself accountable for continual progression (by checking when code is committed and milestones are hit).  For hosting, I currently have a web hosting account through A Small Orange which I will be evaluating to see if that is sufficient for running the website on; due to the application I am planning to build being a Node.js application which also requires an Elasticsearch document repository for the annotations, I may need to search out other hosting options.  During much of development though, I can run the entire application locally on my laptop.

In terms of risks, there is a risk to the project related to video hosting; the large filesize of many of the videos I wish to upload could become very expensive to pay for hosting for, and so free/alternative hosting solutions should be investigated.  As the prototype is intended primarily to be a "proof-of-concept" and not necessarily a commercially viable product for the market the potential problem of where to host the videos is not a grave risk, but is an important consideration.  Currently I intent to research and assess the suitability of a few different video hosting platforms that could be leveraged for the project that would involve minimal or no cost, such as YouTube.  There may also be a scope risk in that adding some of the nicer features of the Requirements, such as giving users the ability to create video playlists.  As I embark on the development phase of the project I will need to re-assess the viability of completing some of more advanced features in the context of the overall goal of making a rich video annotation prototype.






%\section{Risks and Alternatives Section 1}
%\label{sec:risksandalternatives:sec1}
%
%\Blindtext[2][2]
%
%\section{Risks and Alternatives Section 2}
%\label{sec:risksandalternatives:sec2}
%
%\Blindtext[3][2]
%
%\section{Risks and Alternatives Section 3}
%\label{sec:risksandalternatives:sec3}
%
%\Blindtext[4][2]
%
%\section{Risks and Alternatives Conclusion}
%\label{sec:risksandalternatives:conclusion}
%
%\Blindtext[2][1]
