% !TEX root = ../dkilleffer-thesis-proposal.tex
%
\chapter{Problem Statement}
\label{sec:problem-statement}

\cleanchapterquote{You can’t do better design with a computer, but you can speed up your work enormously.}{Wim Crouwel}{(Graphic designer and typographer)}

%\Blindtext[2][2]

%
%\section{Postcards: My Address}
%label{sec:intro:address}
%
%\textbf{Ricardo Langner} \\
%Alfred-Schrapel-Str. 7 \\
%01307 Dresden \\
%Germany
%

\section{Motivation and Problem Statement}
\label{sec:problem-statement:motivation}

%\Blindtext[3][1] \cite{Jurgens:2000,Jurgens:1995,Miede:2011,Kohm:2011,Apple:keynote:2010,Apple:numbers:2010,Apple:pages:2010}

%\section{Results}
%\label{sec:intro:results}
%
%\Blindtext[1][2]

Several years ago my siblings and I lost our two remaining grandparents; my maternal grandmother, and my paternal grandfather, both within a couple years of each other.  These were difficult losses to take, and I was left thinking of them often and the times we had together.  At the same time, I was recently married and had started a family of my own, and enjoying all the highs, lows, and excitement of being a part of a young family with children.  With sentimentality creeping into my mind more and more, we would often videotape our young son, and then his younger brother, and making memories with our children and saving them to video for posterity.  Several years later I found myself with a very large collection of both VHS and Mini-DV tapes (well over a hundred tapes, at least), and I realized that my wife, kids, and I had not viewed most of these recordings, not even since they were originally taped.  At an extended family dinner I inquired about all the old VHS tapes my parents had recorded of us kids growing up, including several important family milestones and a few select events that my grandparents would have been a part of; I was told that I was free to take any videotapes I could find.  I did the same thing with my in-laws and gathered up all their old videotapes as well; soon I found myself in the posession of a virtual mountain of videotapes, some up to 25 years old.  I knew that over time videotapes degrade and are subject to a process of "vinegarization" (see \url{http://www.clir.org/pubs/reports/pub54/2what_wrong.html} and \url{http://www.emeraldartservices.com/visual-media-deterioration/}), and I knew that if I wanted to preserve all the precious memories that were captured on those tapes that I would need to digitize this collection.

Thus began a process of over a year's worth of work whereby I slowly digitized nearly 200 analogue tapes of various formats; VHS, Mini-DV, VHS-C, etc.  Initially I was tempted to edit and cleanup the recordings as I imported them, but soon I found out just how much time and effort is involved in doing high-quality video editing and cleanup, and I realized I would never finish digitizing the tape collection if I stopped digitizing to edit each tape.  Eventually I was able to successfully digitize about 99\% of the videotape collection, and I was left with an enormous set of video files (one per tape).  Some statistics of the collection:

\begin{itemize}
\item TODO: number of video files
\item TODO: total disk size of all video files
\item TODO: total number of hours of recordings
\end{itemize}

While I certainly loved being able to go back and re-live many funny childhood moments that were now immortalized on an external hard drive, I quickly came to realize several things about my new massive video file collection:

\begin{enumerate}
\item I did not know who was in several of the videos, but I knew that my mom/my dad/my father-in-law/my uncle/etc. would know
\item I did not know when many of the recordings took place
\item I did not know where some of the recordings were made
\item It was extremely difficult and time-consuming to be able to properly share old historical family moments from the video collection with the family because the videos were only labeled by type (VHS, Mini-DV, etc.) and tape number
\end{enumerate}

The last point is perhaps the most poignant. In my eagerness and excitement to share my newfound digital video treasure trove with my family, I fumbled at several family dinners and gatherings when I was requested to play the \textit{"funny barbecue video from 1987 where Nate accidentally hit cousin Al in the head"}, and several other classic family gems; I simply couldn't find videos that I was looking for without basically brute-forcing my way and playing each video, fast-forwarding through the video until either I found (or did not find) what I was looking for, and then wrote down what video and at what time "that moment" that I was looking for was found in.  The problem was that despite having invested over a year's worth of time and effort into preserving all these old family videos, it wasn't worth much to everybody else (or me!) in their current form \textit{\textbf{because nobody could find what they actually wanted to see without watching the entire collection}}.  And this revelation was the genesis of my thesis idea; to create a platform where I could leverage the knowledge and memories of my family to help me build up a set of rich metadata to annotate the family video collection, and then to reward them for their help in annotating the videos by building out a rich, faceted search interface to the video collection, as well as creating the ability to create "playlists" where users can make their own "highlight reels" of special moments, people, places, etc.



%
%
%
%\subsection{Some References}
%\label{sec:problem-statement:results:refs}
%\cite{WEB:GNU:GPL:2010,WEB:Miede:2011}
%
%\section{Thesis Structure}
%\label{sec:problem-statement:structure}
%
%\textbf{Chapter \ref{sec:related}} \\[0.2em]
%\blindtext
%
%\textbf{Chapter \ref{sec:system}} \\[0.2em]
%\blindtext
%
%\textbf{Chapter \ref{sec:concepts}} \\[0.2em]
%\blindtext
%
%\textbf{Chapter \ref{sec:concepts}} \\[0.2em]
%\blindtext
%
%\textbf{Chapter \ref{sec:conclusion}} \\[0.2em]
%\blindtext
%


