% !TEX root = ../dkilleffer-thesis-proposal.tex
%
\pagestyle{empty}
\hfill
\pdfbookmark[0]{Glossary}{Glossary}
\section*{Glossary}

%You should not assume that all readers are familiar with the technology or terminology referred to in your thesis proposal.  This section should include definitions of major terms and an explanation of acronyms.

Here are some of the terms used throughout this proposal.

\begin{itemize}[leftmargin=*]
\label{glossary:amazon-x-ray}
\item \textbf{Amazon X-Ray} \\
	a reference tool incorporated into several video players that allows for the display and linking of actors, acresses, directors, and linked data when viewing a movie or television show hosted by Amazon. (see \url{https://en.wikipedia.org/wiki/X-Ray_%28Amazon_Kindle%29}, \url{http://www.amazon.com/gp/help/customer/display.html?nodeId=201423010})
\label{glossary:apache-solr}
\item \textbf{Apache Solr} \\
	a popular, open-source fast document-oriented search engine similar to ElasticSearch, which is likewise built on top of the Apache Lucene engine (see \url{http://lucene.apache.org/solr/})
\label{glossary:bootstrap}
\item \textbf{Bootstrap} \\
	A popular open-source framework used to speed up development of websites by supporting HTML, CSS, and JavaScript and supplying a responsive, mobile-ready layout mechanism. (see \url{http://getbootstrap.com/}).
\label{glossary:dvd}
\item \textbf{DVD} \\
	abbreviation of "Digital Video Disc", these are digital discs similar in size to CDs but can store much more information and were first used primarily for video content, but later gained popularity for storing data files as well.  DVDs were first sold in 1997 and soon became wildly popular, largely supplanting VHS as the primary delivery mechanism for movies.
\label{glossary:elasticsearch}
\item \textbf{Elasticsearch} \\
	a fast document-oriented search engine also based upon the open-source information retrieval library Lucene (similar to Apache Solr).  ElasticSearch achieves high speed data retrieval due to searching indexed data fields rather than searching text directly, and is a competing product to Apache Solr. (see \url{https://en.wikipedia.org/wiki/Elasticsearch}. \url{http://www.elasticsearchtutorial.com/basic-elasticsearch-concepts.html})
\label{glossary:express.js}
\item \textbf{Express.js} \\
	a minimal and flexible framework for building web applications and APIs under Node.js.  (see \url{https://expressjs.com/})
\label{glossary:faceted-search}
\item \textbf{faceted search} \\
	a search technique that categorizes items into "buckets" (e.g., facets) that allow for drill-down searches into distinct and more specific categories.  An example of a faceted search would be the various distinct and increasingly specific product categories/specifications for a product item search on Amazon; for example, when searching for men's shoes, facets can be broken down by shoe size, color, style, manufacturer, purpose, etc.
\label{glossary:json}
\item \textbf{JSON} \\
	a human-readable, text-based format for documents that is also machine-parseable.  JSON documents are structured as \textit{key:value} pairs, where the \textit{value} can be an array, a single text string, or another JSON document entirely. 
\label{glossary:node.js}
\item \textbf{Node.js} \\
	a JavaScript runtime built on \href{https://developers.google.com/v8/}{Chrome's V8 JavaScript engine}, Node.js allows you to run JavaScript on the server-side, and build a wide variety of applications using JavaScript as the primary language. (see \url{https://nodejs.org/en/})
\label{glossary:mini-dv}
\item \textbf{Mini-DV} \\
	a successor to the wildly popular VHS home recording system, Mini-DV is a cassette tape format for video recording. It captures video in a resolution close to that of DVD. (see \url{http://techterms.com/definition/minidv})
\label{glossary:react.js}
\item \textbf{React.js} \\
	an open-source JavaScript library for building user interfaces, originally developed and used by \href{http://www.facebook.com/}{Facebook}. (see \url{https://facebook.github.io/react/})
\label{glossary:restful-api}
\item \textbf{RESTful API} \\
	"an application program interface that uses HTTP requests to GET, PUT, POST, and DELETE data" (see \url{http://searchcloudstorage.techtarget.com/definition/RESTful-API})
\label{glossary:vhs}
\item \textbf{VHS} \\
	acronnym for "Video Home System", it is a widely-adopted videocassette recording ( VCR ) technology that was developed by Japan Victor Company (JVC) and put on the market in 1976. It uses magnetic tape 1/2 inch (1.27 cm) in width.  It was extremely popular in the 1980s and 1990s, and declined in use during the early 2000s. (adapted from \url{http://whatis.techtarget.com/definition/VHS-Video-Home-System} and \url{https://en.wikipedia.org/wiki/VHS})
\end{itemize}
